Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
On cascade

@@

@@

For now, assume $\alpha=1$ (not to deal with inter-component communication).
Consider an algorithm DET2, a modified version of DET from \cite{repartition-disc}.
Modification is the following: when repartition is necessary, move to \emph{the closest} perfect partition of components.

Now we bound the cost of a single repartition of DET2 independent of $\ell$.
First, we bound the cycle length in one of optimal solutions.

@@

\begin{theorem}
  \label{th:cascade-cycles}
  Consider a single repartition of DET2 caused by node merge.
  There exists a sequence of node migrations that realizes this repartition, where each node-disjoint cycle has length at most $k$.
\end{theorem}
Describe the graph. Edges and labels.

@@

\begin{proof}
\end{proof}

@@

\begin{proof}
  Each node has degree at most $k$. Combine with Theorem \ref{th:cascade-cycles}.

Important technical details:
\begin{itemize}
  \item There are no cycles attached to another cycles by just one vertex (by equivalent signature skipping). This is important, as otherwise we just have a bound on cycles, but the graph contains a chain of cycles.
  Another formulation (Stefan's): each edge is a part of a cycle that goes through the "origin" part of the graph.
\end{itemize}
\end{proof}

>>>>

\maciek{Emphasize the difference to DET: "Modification is the following: when repartition is necessary, move to \emph{the closest} perfect partition of components."}

@@

Describe the graph. Edges and labels.

@@

Now we bound the cost of a single repartition of DET2 independent of $\ell$.
First, we bound the length of each path in one of optimal solutions.

@@

\begin{theorem}
  \label{th:cascade-paths}
  Consider a single repartition of DET2 caused by node merge.
  There exists a sequence of node migrations that realizes this repartition, where each node-disjoint cycle has length at most $k$.
\end{theorem}

\begin{proof}

@@

@@

\begin{proof}
  Each node has degree at most $k$. Combine with Theorem \ref{th:cascade-paths}.
